---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```


# kesernetwork

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

## Overview

The kesernetwork builds a shiny app to visualize the knowledge networks for the code concepts. Using co-occurrence matrices of EHR codes from Veterans Affairs (VA) and Massachusetts General Brigham (MGB), the knowledge extraction via sparse embedding regression (KESER) algorithm was used to construct knowledge networks for the code concepts.

## Installation


Or install the development version from GitHub with:

``` r
install.packages("remotes")
remotes::install_github("celehs/kesernetwork", repo = "linkage")
```



## Usage

This is a basic example which shows you how to run the `kesernetwork` app. Remember you need to get access to the data and save it to your local computer. In order to guarantee some dependencies are loaded, you must use `library(kesernetwork.linkage)` beforehand, instead of directly running `kesernetwork.linkage::run_app()`.


```{r eval=FALSE}
library(kesernetwork.linkage)
run_app(Rdata_path = "path/to/kesernetwork.RData")
```



See the [getting started guide](https://celehs.github.io/kesernetwork/articles/main.html)
to learn how to use kesernetwork.



## Citations

- Hong, C., Rush, E., Liu, M. et al. Clinical knowledge extraction via sparse embedding regression (KESER) with multi-center large scale electronic health record data. npj Digit. Med. 4, 151 (2021). https://doi.org/10.1038/s41746-021-00519-z

